Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2012-12-23 docs/tex/draft.tex
Added some comments about theoretical details

>>>>

\subsection{Theory Notes}

\paragraph{Failure Cases} : Here we list some of the failure cases : 
\begin{itemize}
\item Can you prove that the number of points on the convex frontier are not exponential ?
\item This algorithm is slow when the points on the frontier resemble the circumeference of a circle
\end{itemize}

\paragraph{More than 2 states } : how does the convex hull algo work for more than 2 states ? How do you calculate the slope of a 3 dimensional polytope ?

\paragraph{convex combinations?} : Does $\theta_A$ and $\theta_B$ need to sum to one?
